An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-15 paper/paper.tex
Paper: Write System Design Overview, all System Design Figure

\section{System Design}
\subsection{Overview}

%Diagram of system design

>>>>

\section{System Design}
\subsection{Overview} \label{subsec:Overview_sec:SystemDesign_chap:Implementation}
%Diagram of system design
We have designed our system to be modular. We realize that future work on our system might include the replacement of our data and metadata layers. Our solution for making these parts interchangeable with different implementations is to define standard interfaces between the two layers, which can be followed to create new implementations for the two layers. Along with these two layers, there is one more major part to our application: the system core. The system core comprises the core functionality of our system, which includes accepting and executing user commands, receiving network requests from other peers, and maintaining the P2P system.

\begin{figure} \label{fig:SystemDesign}
  \centering
  \includegraphics[scale=0.4]{SystemDesign}
  \caption{The design of our system}
\end{figure}

We explain each of these components in the following sections.
